\maketitle
\makesignature

\ifproject
\begin{abstractTH}
โครงงานนี้เป็นการพัฒนาเกมต้นแบบชื่อ Marionette ซึ่งเป็นเกมแนว 2 มิติประเภท Action RPG ที่ผสมผสานรูปแบบการเล่นแบบ Casual และ Mini-game โดยมีธีมหลักเกี่ยวกับโรงละครหุ่นเชิดที่มีบรรยากาศสดใสแต่แฝงไปด้วยโทนหม่นหมอง ผู้เล่นจะรับบทเป็นมนุษย์ที่ถูกแม่มดจับตัวมาแปลงเป็นหุ่นเชิดเพื่อใช้แสดงในโรงละคร และต้องพยายามหาทางหลบหนีเพื่อกลับคืนสู่อิสรภาพ

ระบบการเล่นของเกมประกอบด้วยหลายส่วนสำคัญ ได้แก่ การสำรวจแผนที่เพื่อเก็บไอเทมและพัฒนาตัวละคร การแสดงบนเวทีในรูปแบบมินิเกมที่มีธีมแตกต่างกันในแต่ละด่าน และการต่อสู้กับบอสเพื่อปลดล็อกความสามารถและดำเนินเนื้อเรื่องของเกม นอกจากนี้ยังมีระบบต่าง ๆ เช่น ระบบค่าสถานะตัวละคร ระบบอุปกรณ์และอาวุธ ระบบคราฟไอเทม รวมถึงระบบบันทึกเกมและระดับความยากที่แตกต่างกัน เพื่อเพิ่มความหลากหลายของประสบการณ์การเล่น

วัตถุประสงค์ของโครงงานนี้คือการพัฒนาเกมต้นแบบที่สามารถเล่นได้จริง โดยเน้นการออกแบบและพัฒนาระบบหลักของเกม เช่น ระบบการต่อสู้ ระบบอินเวนทอรี ระบบศัตรู และระบบบอส พร้อมทั้งออกแบบฉาก ตัวละคร แอนิเมชัน และส่วนติดต่อผู้ใช้ เพื่อให้ผู้เล่นสามารถทดลองรูปแบบการเล่นของเกมได้อย่างสมบูรณ์ในระดับด่านแรก ผลลัพธ์ของโครงงานแสดงให้เห็นแนวทางการออกแบบเกมที่ผสมผสานระหว่างการผจญภัย การต่อสู้ และมินิเกมในธีมโรงละคร ซึ่งสามารถนำไปพัฒนาและต่อยอดเป็นเกมฉบับสมบูรณ์ได้ในอนาคต

\end{abstractTH}

\begin{abstract}
This project focuses on the development of a game prototype titled Marionette, which is a two-dimensional Action RPG that combines casual gameplay elements with mini-games. The main theme of the game revolves around a puppet theater with a bright yet slightly gloomy atmosphere. In the game, the player takes the role of a human who has been captured by a witch and transformed into a marionette puppet to perform in the theater. The player must attempt to escape from the witch’s control and regain their freedom.

The gameplay system consists of several key components. These include map exploration for collecting items and character progression, stage performances presented in the form of mini-games with different themes in each level, and boss battles that allow players to unlock new abilities and progress through the storyline. In addition, the game includes several supporting systems such as character status attributes, equipment and weapon systems, item crafting, a save system, and multiple difficulty levels. These systems are designed to enhance gameplay diversity and provide a more engaging player experience.

The objective of this project is to develop a playable game prototype by focusing on the design and implementation of the core gameplay systems. These systems include the combat system, inventory system, enemy system, and boss system. The project also involves designing game environments, characters, animations, and user interface components to ensure that players can experience the core gameplay mechanics within the first level of the game. The outcome of this project demonstrates an approach to game design that integrates exploration, combat mechanics, and mini-game elements within a theatrical theme. Furthermore, the prototype can serve as a foundation for further development into a complete game in the future.
\end{abstract}

\iffalse
\begin{dedication}
This document is dedicated to all Chiang Mai University students.

Dedication page is optional.
\end{dedication}
\fi % \iffalse

\iffalse
\begin{acknowledgments}
Your acknowledgments go here. Make sure it sits inside the
\texttt{acknowledgment} environment.

\acksign{2020}{5}{25}
\end{acknowledgments}%
\fi

\contentspage

\ifproject
%%\figurelistpage

%%\tablelistpage
%%\fi % \ifproject

% \abbrlist % this page is optional

% \symlist % this page is optional

% \preface % this section is optional
